|

### 2020-09-24 pre-analysis-plan/freire-skarbek-lynching.Rmd
typo

[^thanks]: We thank Rosario Aguilar, Louise Araújo, Miriam Golden, Umberto Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Sacco for their valuable comments.

>>>>

[^thanks]: We thank Rosario Aguilar, Louise Araújo, Miriam Golden, Umberto
Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Scacco for their valuable comments.
